Robot Team III: Scotty Strikes Back

### 2024-05-07 paper/paper.tex
Added sample paragraph 3

% 3. Unsupervised ML
To complement these capabilities...

Therefore, unsupervised techniques to segment HSI and identify unique spectral signatures are needed for near-real time applications where detailed knowledge of contaminants may not be available

@@

>>>>

% 3. Unsupervised ML

% To take full advantage of the information contained in HSI for near-real time water quality analysis, unsupervised methods that segment HSI pixels and can extract relevant spectral endmembers are needed.

% A variety of technqiues have

% Data-driven techniques such as principal component analysis (PCA), independent component analysis (ICA), and k-nearest neighbors (kNN) have been widely employed for HSI analysis \cite{yousefi2016mineral,} (other citations). While useful, these methods

% Geometric methods such as vertex component analysis (VCA) offer another approach based on the fact that endmember spectra form vertices of a simplex \cite{}. However, these approaches

% Deep learning strategies such as autoencoders...

% Principal component analysis (PCA) has been widely used for this task as it enables both dimensionality reduction and feature extraction.

% Principal component analysis (PCA) is a popular choice for both dimenionsality reduction and feature extraction.

% Principal component analysis (PCA) is a common method utilized for both dimensionality reduction and feature extraction

Unsupervised machine learning (ML) approaches have been widely explored for hyperspectral image (HSI) analysis, including dimensionality reduction, unsupervised classification, and endmember extraction and spectral unmixing. Dimensionality reduction techniques, such as principal component analysis (PCA) and t-Distributed Stochastic Neighbor Embedding (t-SNE), aim to represent the high-dimensional HSI data in a lower-dimensional space while preserving relevant information. However, PCA is a linear model, and t-SNE can be computationally complex. Unsupervised classification methods, including k-nearest neighbors (k-NN), fuzzy c-means, DBSCAN, matrix factorizations, and autoencoders, can identify clusters in the data, but do not directly aid in visualization. Robust Manifold Matrix Factorization has been used for both dimensionality reduction and clustering, while convolutional autoencoders with softmax have been employed for endmember extraction and unmixing. Additionally, stacked autoencoders and variational autoencoders (VAEs) have been combined for unmixing tasks. Endmember extraction and spectral unmixing techniques, such as geometric and statistical methods, vertex component analysis, and non-negative matrix factorization (NMF), have been widely explored. While these methods can identify relevant endmembers, they often rely on the presence of pure pixels or require prior knowledge of the number of endmembers, which may not be valid in certain scenarios. Once endmembers are identified, abundance maps can be produced using techniques like spectral angle mapper or unmixing assuming a mixing model, but these do not directly facilitate visualization. The increased spatial resolution afforded by unmanned aerial vehicle (UAV) platforms suggests that UAV-based HSI is ideal for endmember extraction, as the likelihood of pure endmembers is significantly higher than in satellite imagery. Consequently, unmixing of UAV-HSI has been used to discover endmembers for satellite HSI or as an endmember library. The goal is to develop a principled method that simultaneously enables dimensionality reduction and classification/endmember extraction for HSI analysis.

@@

Among unsupervised methods, Kohonen's self-organizing map provides an attractive compromise enabling both dimensionality reduction and classification...
